

## Loading the data When loading the dataset into R, please consider the following:

  - The dataset has 2,075,259 rows and 9 columns. 
-calculate a rough estimate of how much memory the dataset will require in memory before reading into R. Make sure your computer has enough
memory (most modern computers should be fine).
  - data from the dates 2007-02-01 and 2007-02-02. 
# subset the dataset to data when Date between 2007-02-01 & 2007-02-02
data <- subset(data, subset = (Date >= "2007-02-01" & Date <= "2007-02-02"))


 -convert the Date and Time variables to Date/Time classes in R using the `strptime()` and `as.Date()`
functions.
# add variable data time that with date & time both
data$datetime <- strptime(paste(data$Date, data$Time), "%Y-%m-%d %H:%M:%S")

  - Note that in this dataset missing values are coded as `?`.

data$datetime <- as.POSIXct(data$datetime)

```{r, eval = FALSE}
download.file('https://d396qusza40orc.cloudfront.net/exdata%2Fdata%2Fhousehold_power_consumption.zip',
              destfile = './hw1_data.zip', method = 'curl', quiet = T)
unzip(zipfile = 'hw1_data.zip')
```

```{r}
rawData <- read.table('household_power_consumption.txt', header = T, stringsAsFactors = F,
                      na.strings = "?", sep = ';', quote = "", skip = 66636, nrows = 2880)
tail(rawData, 10)
colnames(rawData) <- c('Date', 'Time', 'GlobalActivePower', 'GlobalReactivePower', 'Voltage',
                       'GlobalIntensity', 'SubMetering1', 'SubMetering2', 'SubMetering3')
rawData$DateTime <- strptime(paste(rawData$Date, rawData$Time), format = '%d/%m/%Y %H:%M:%S')
```

## Making Plots

Our overall goal here is simply to examine how household energy usage varies over a 2-day period in February, 2007. Your task is to
reconstruct the plots that can be found [here](https://github.com/rdpeng/ExData_Plotting1), all of which were constructed using the base plotting system.

plotting

  - Construct the plot and save it to a PNG file with a width of 480 pixels and a height of 480 pixels.
  - Name each of the plot files as `plot1.png`, `plot2.png`, etc.
  - Create a separate R code file (`plot1.R`, `plot2.R`, etc.) that constructs the corresponding plot, i.e. code in `plot1.R` constructs
the `plot1.png` plot. Your code file **should include code for reading the data** so that the plot can be fully reproduced. You should also
include the code that creates the PNG file.
  - Add the PNG file and R code file to your git repository

### Plot 1
```{r}
#png('plot1.png', width = 480, height = 480)
hist(rawData$GlobalActivePower, col = 'red',
     main = 'Global Active Power',
     xlab = 'Global Active Power (kilowatts)')


# Save plot to png file plot1.png with width & height equal 480px
dev.copy(png, file = "plot1.png", width=480, height=480)
dev.off()
```

### Plot 2
```{r}
#png('plot2.png', width = 480, height = 480)
plot(x = rawData$DateTime, y = rawData$GlobalActivePower, 
     type = 'l', xlab = NA, ylab = 'Global Active Power (kilowatts)')

# Save plot2
dev.copy(png, file = "plot2.png", height = 480, width = 480)

#dev.off()
```

### Plot 3
```{r}
#png('plot3.png', width = 480, height = 480)
plot(x = rawData$DateTime, y = rawData$SubMetering1, type = 'l',
     xlab = NA, ylab = 'Energy sub metering')
lines(x = rawData$DateTime, y = rawData$SubMetering2, col = 'red')
lines(x = rawData$DateTime, y = rawData$SubMetering3, col = 'blue')
legend('topright', 
       legend = c('Sub_metering_1', 'Sub_metering_2', 'Sub_metering_3'),
       col = c('black', 'red', 'blue'),
       lwd = 1)

# Save plot3
dev.copy(png, file = "plot3.png", height = 480, width = 480)
dev.off()
```

### Plot 4(grid)
```{r}
#png('plot4.png', width = 480, height = 480)
par(mfrow = c(2, 2)) 
  #plots from left to right, top to bottom (since you used mfrow vs mfcol)

#plot 
plot(x = rawData$DateTime, y = rawData$GlobalActivePower, 
     type = 'l', xlab = NA, ylab = 'Global Active Power')

#plot 
plot(x = rawData$DateTime, y = rawData$Voltage, 
     type = 'l', xlab = 'datetime', ylab = 'Voltage')

#plot
plot(x = rawData$DateTime, y = rawData$SubMetering1, type = 'l',
     xlab = NA, ylab = 'Energy sub metering')
lines(x = rawData$DateTime, y = rawData$SubMetering2, col = 'red')
lines(x = rawData$DateTime, y = rawData$SubMetering3, col = 'blue')
legend('topright', 
       legend = c('Sub_metering_1', 'Sub_metering_2', 'Sub_metering_3'),
       col = c('black', 'red', 'blue'),
       lwd = 1, bty = 'n')

#plot 
plot(x = rawData$DateTime, y = rawData$GlobalReactivePower, type = 'l',
     xlab = 'datetime', ylab = 'Global_reactive_power')

# Save to plot4.png file

dev.copy(png, "plot4.png", width=480, height=480)
dev.off()
```
